Size matters: Divergent morphology in elliptical bifaces from sites in the American Southeast articulates with distinct local reduction practices

### 2022-08-08 supp/index.Rmd
<edit index>

American Southeast, Caddo, Jowell biface, lithics, archaeology, archaeoinformatics, museum studies, digital humanities, geometric morphometrics, STEM, STEAM

>>>>

American Southeast, Caddo, archaeology, archaeoinformatics, museum studies, digital humanities, geometric morphometrics, STEM, STEAM, Jowell biface, lithics, parallel-oblique flake scars
